---
title: "Gromacs force field"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The Amber force field files for Amino acid, dna, rna, and ions are downloaded to use with Gromacs. For dna(rna), there are 4 different types of files. dna.arn, dna.hdb, dna.r2b, dna.rtp. Of these files, dna.arn, dna.r2b seems to be useless, just some information file. dna.hdb has some information which I do not understand, maybe it is some information about the constraint? dna.rtp has the definition the dna base pairs: the compostion of the molecule, the interactions and bonds between atoms in the molecule.  

Now I have found out that **hdb** file is hydrogen database, should not be necessary in my case.

ffbonded.itp has all the parameters for the bond interaction.
ffnonbonded.itp has all the parameters for the nonbonded interaction.

atomtypes.atp has the definition for the atom types used in the forcefield.

I took out the base pair part of the nucleotide A. As one can see the total charge of the base pair part is not zero. Is this a big problem?
```{r}
library(tidyverse)
a <- read_table("A.txt", col_names = FALSE)
sum(a$X3)

```
If we add an H atom (the **H1** atom defined in the force field), the charge will be nearly zero. 

We can do the same thing for nucleotide T
```{r}
t <- read_table("T.txt", col_names = FALSE)
sum(t$X3)

```


We  can do the same thing for nucleotide G
```{r}
G <- read_table("G.txt", col_names = FALSE)
sum(G$X3)

```


We can do the same thing for nucleotide C
```{r}
C <- read_table("C.txt", col_names = FALSE)
sum(C$X3)

```

Improper interaction are a spiecial (or normal?) type of dihedral interaction. It constraints the angle between two planes using harmonic potential.

(The proper dihedral interactions are periodic)

The same atom can have different charges in the rtp file, which might be OK, since the ffbonded.itp and ffnonbonded itp has no charge information? (ffnonbonded.itp has a charge parameter, but is set to 0 for all the atoms. So I presume that the charge will be overiden in the rtp file.)

Use a hydrogen atom to replace **C1** might be better.
